---
title: "HW3"
author: "Kara Godsey, Deep Sagar Karki"
date: "3/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load, include=FALSE}
library (tidyverse)
library(dplyr)
library(knitr)
library(survey)
library(sampling)
library(ggplot2)
```

### Question 1

Using the Corona Virus data file, take 100 different simple random samples of 58 countries without replacement using the random seeds numbered 101 through 200. With each sample do the following:

```{r a}
load("~/R/STAT5060/5060hw3/corona330.RData")
cor <- corona330[,c(1,2,3,6)]
colnames(cor) <- c("Province.State","Country.Region","Cases","Deaths")
N <- length(unique(cor$Country.Region))
cor$fpc <- N
n <- 58

totx_a <-rep(NA,100)
bias_a <-rep(NA,100)
re_a <- rep(NA,100)
bias_re <- rep(NA,100)
thatr_a <- data.frame(1:100,1:2)
colnames(thatr_a)<-c("REtotest","SE")

#actual death count
truetotdeath <- sum(cor$Deaths)


for(i in 101:200){
  set.seed(i)
  corsamp <- cor[sort(sample(N,n)),]
  corsampdes <- svydesign(id = ~1, strata = NULL, data = corsamp, fpc = ~fpc)
  sampdeathtot <- svytotal(~Deaths, design=corsampdes, na.rm=TRUE)
  bias <- sampdeathtot - truetotdeath
  bias_a[i-100] <- bias
  totx_a[i-100] <- sampdeathtot
  ratestdeath <- svyratio(~Deaths, ~Cases, corsampdes)
  re_a[i-100] <- ratestdeath$ratio
  thatr <- predict(ratestdeath,total = sum(cor$Cases),se=TRUE)
  retotal <- as.numeric(thatr$total)
  thatr_a[i-100,1] <- retotal
  thatr_a[i-100,2] <- as.numeric(thatr$se)
  bias_ratio <- retotal - truetotdeath
  bias_re[i-100] <- bias_ratio
}

totx_a<-data.frame(totx_a)
bias_a<-data.frame(bias_a)
bias_re<-data.frame(bias_re)
re_a<-data.frame(re_a)
totre <- data.frame(thatr_a[,1])
colnames(totre) <- "TotRE"

totaplot <- ggplot(totx_a,aes(totx_a)) + geom_histogram(bins=30) + labs(title = "Basic Estimation")

biasaplot <- ggplot(bias_a,aes(bias_a)) + geom_histogram(bins=30) + labs(title = "Basic Estimation")

biasreplot <- ggplot(bias_re,aes(bias_re)) + geom_histogram(bins=30) + labs(title = "Ratio Estimation")

var_a<-var(totx_a)

totreplot <- ggplot(totre,aes(x=TotRE))+ geom_histogram(bins=30) + labs(title = "Ratio Estimation")

avgbias1 <- mean(bias_a[,1])

avgbias2 <- mean(bias_re[,1])

avgbias <- merge(avgbias1,avgbias2)
colnames(avgbias) <- c("totx_a","TotRE")

variance1 <- var(totx_a)
variance2 <- var(totre)

variance_est <- merge(variance1, variance2)

partf <- rbind(avgbias,variance_est)
rownames(partf) <- c("Average Bias", "Variance")
colnames(partf) <- c("Estimate 1", "Estimate 2")

MSE_me <- variance1 +(avgbias1^2)

MSE_re <- variance2 + (avgbias2^2)

MSE <- merge(MSE_me,MSE_re)
rownames(MSE) <- "MSE"
colnames(MSE) <- c("Mean estimator", "Ratio estimator")
```

***Part a***

***Estimate the total number of deaths in the World as a result of the Corona Virus assuming you know the number of countries to be that contained in the data file.***

With this assumption, we find the number of countries by finding the number of unique values in the Country column of our dataset. The number of countries in the data set is then found to be the following.

```{r b,include=TRUE}
N
```

***Part b***

The actual death total is found by summing up the deaths contained in our population file.

```{r c, include = TRUE}
truetotdeath
```

This number is utilized to calculate the bias of each sample, which will be evident in the appendix of code as well as the graphs.

***Part c and part d***

The mechanics of these parts can be seen in the appendix of code, with the outputs represented in the graphs shown for part e.

***Part e***

First we will show histograms for estimates of the total number of deaths in the world as a result of the coronavirus. 

The graph on the left depicts our basic estimation of a total with an SRS. The graph on the right depicts the total derived from ratio estimation, where the number of cases confirmed is used as the auxiliary variable.

```{r d,fig.show="hold", out.width="50%"}
totaplot
totreplot
```

Now we will show the comparison of bias in each of the two estimations.

```{r e,fig.show="hold", out.width="50%"}
biasaplot
biasreplot
```

**Part f**

The average bias as well as the variance for each of the estimates are given below where Estimate 1 represents the basic estimate and Estimate 2 represents the estimate computed using ratio estimation.

```{r f}
kable(round(partf,digits=1))
```

**Part g**

Below is the Mean Squared Error for each estimator.

```{r g}
kable(MSE)
```

**Part h**

The result in part g makes sense. We would expect the error to be lower for ratio estimation, since we expect that there is a relationship between cases and deaths in the population.

**CODE**

```{r appendix1, ref.label=c('a'), echo=TRUE}

```

### Question 2

**CODE**

```{r appendix2, ref.label=c(), echo=TRUE}

```

### Question 3

**CODE**

```{r appendix3, ref.label=c(), echo=TRUE}

```